Code walkthrough

### 2022-10-06 src/explore_aghq/walkthrough.Rmd
silent = TRUE to make this more readable

---
title: "Code walkthrough"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**

  **Task**
---

In this section, we will step through some of the functions in `aghq` to make sure we understand them.
We will use the epilepsy example, explained in more detail in the [`epil`](https://athowes.github.io/elgm-inf/epil.html) notebook.

@@

obj <- MakeADFun(
  data = dat,
  parameters = param,
  random = c("epsilon", "nu"),
  DLL = "epil"
)
```
# `aghq::marginal_laplace_tmb`

Start by calling this function, to show where we're trying to end up:

```{r}
fit <- aghq::marginal_laplace_tmb(
  obj,
  k = 2,
  startingvalue = c(param$beta, param$l_tau_epsilon, param$l_tau_nu)
)

summary(fit)
```

@@

#' Hessian
if (control$numhessian) {
  ff$he <- function(theta) numDeriv::jacobian(ff$gr, theta, method = "Richardson")
}

#' Now we're going to do the AGHQ
quad <- aghq(
  ff = ff,
  k = k,
  transformation = transformation,
  startingvalue = startingvalue,
  optresults = optresults,
  basegrid = basegrid,
  control = control
)

#' There is an option whereby quad will just return the normalising constant, and if so then tmb_marginal_laplace can also be used
#' just to return the normalising constant too. Note on this, why use tmb_marginal_laplace in this situation rather than aghq? Since
#' as far as I understand we're not doing the marginal laplace approximation if control$onlynormconst is TRUE
if (control$onlynormconst) return(quad)

## Add on the info needed for marginal Laplace ##
# Add on the quad point modes and curvatures

>>>>

---
title: "Code walkthrough"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** The `aghq` package implements adaptive Gaussian Hermite quadrature. It is particularly compatible with the `TMB` package for Laplace approximations.

  **Task** In preparation for implementing new methods into `aghq`, in this notebook we walkthrough various `aghq` functions. This will improve understanding of (1) the method, and (2) how to manipulate `TMB` objects in R.
---

We use the epilepsy example, explained in more detail in the [`epil`](https://athowes.github.io/elgm-inf/epil.html) notebook, as example.
Start by loading and preparing the data, as well as compling the `TMB` template:

@@

obj <- MakeADFun(
  data = dat,
  parameters = param,
  random = c("epsilon", "nu"),
  DLL = "epil",
  silent = TRUE
)
```

# `aghq::marginal_laplace_tmb`

We start by calling this function, to show where we're trying to end up:

```{r results='hide'}
fit <- aghq::marginal_laplace_tmb(
  obj,
  k = 2,
  startingvalue = c(param$beta, param$l_tau_epsilon, param$l_tau_nu)
)
```

```{r}
summary(fit)
```

@@

#' Hessian
if (control$numhessian) {
  ff$he <- function(theta) numDeriv::jacobian(ff$gr, theta, method = "Richardson")
}
```

```{r results='hide'}
#' Now we're going to do the AGHQ
quad <- aghq(
  ff = ff,
  k = k,
  transformation = transformation,
  startingvalue = startingvalue,
  optresults = optresults,
  basegrid = basegrid,
  control = control
)
```

```{r}
#' There is an option whereby quad will just return the normalising constant, and if so then tmb_marginal_laplace can also be used
#' just to return the normalising constant too. Note on this, why use tmb_marginal_laplace in this situation rather than aghq? Since
#' as far as I understand we're not doing the marginal laplace approximation if control$onlynormconst is TRUE
if (control$onlynormconst) return(quad)
